Multi-level modeling with Openflexo/\FML

### 2022-03-31 7-requirementssatisfaction.tex
clarification

In the previous Sect.~\ref{sec:model}, we demonstrated that our solution
satisfies all the challenge requirements. In this section, we summarize the
different techniques used to satisfy them, without repeating all the
justifications. We classify these techniques into three categories:
\begin{itemize}
    \item \emph{syntactic conformance}: the requirements are structurally
      satisfied when the model conforms to its metamodel,
    \item \emph{constraints checking}: the requirements are fulfilled when all
      instances satisfy both syntactic conformance and the evaluation of
      invariants expressed for related concepts,
    \item \emph{tooling}: the requirements are enforced by the implementation
      of the associated tool.
\end{itemize}

@@

\renewcommand{\arraystretch}{1.1}
\begin{table*}
 \centering
 \rowcolors{4}{tableShade}{white}  %% start alternating shades from 3rd row
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
   \hline
    & \multicolumn{6}{c|}{Syntactic conformance} & Constraints & \multirow{2}{*}{Tooling}\\
   \cline{1-7}
                 & Conc.      & Spec.      & Comp.      & L.Inst.     & O.Inst.     & B.Mod.   &  checking & \\
  \hline
    \reqp{1}  & \checkmark &            & \checkmark &            &            &            &            & \\
    \reqp{2}  & \checkmark & \checkmark & \checkmark &            &            &            &            & \\
    \reqp{3}  &            &            & \checkmark &            &            &            &            & \\
    \reqp{4}  & \checkmark &            &            &            & \checkmark &            &            & \\
    \reqp{5}  & \checkmark &            & \checkmark &            &            &            &            & \\
    \reqp{6}  & \checkmark &            & \checkmark &            &  &            &            & \\
    \reqp{7}  & \checkmark &            & \checkmark &            &            &            &            & \\
    \reqp{8}  &            &            & \checkmark &            &            &            &            & \\
    \reqp{9}  &            &            & \checkmark &            &            &            & \checkmark & \\
    \reqp{10} & \checkmark &            &            &            & \checkmark &            &            & \\
    \reqp{11} & \checkmark &            & \checkmark &            & \checkmark &            &            & \\
    \reqp{12} &            &            & \checkmark &            &            &            &            & \\
    \reqp{13} & \checkmark &            & \checkmark &            & \checkmark &            &            & \\
    \reqp{14} & \checkmark &            &            &            & \checkmark &            &            & \\
    \reqp{15} & \checkmark &            &            &            & \checkmark &            &            & \\
    \reqp{16} & \checkmark &            &            &            & \checkmark &            &            & \\
    \reqp{17} & \checkmark           &            &            &            &            & \checkmark & \checkmark & \checkmark \\
    \reqp{18} & \checkmark           &            &            &            &            & \checkmark &            & \\
    \reqp{19} &            & \checkmark & \checkmark &            &            & \checkmark &            & \\
  \hline
\end{tabular}
     \caption{Requirements satisfaction for base metamodel}
    \label{tab:RequirementsSatisfactionBaseMetamodel}
\end{table*}

\begin{table*}
 \centering
  \rowcolors{4}{tableShade}{white}  %% start alternating shades from 3rd row
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
   \hline
    & \multicolumn{6}{c|}{Syntactic conformance} & Constraints & \multirow{2}{*}{Tooling}\\
   \cline{1-7}
                 & Conc.      & Spec.      & Comp.      & L.Inst     & O.Inst     & B.Mod      & checking   & \\
  \hline
    \reqs{1}  &            &            &            & \checkmark &            &            &            & \\
    \reqs{2}  &            &            &            & \checkmark &            &            &            & \\
    \reqs{3}  & \checkmark & \checkmark & \checkmark & \checkmark &            &            &            & \checkmark \\
    \reqs{4}  & \checkmark & \checkmark & \checkmark & \checkmark &            &            &            & \\
    \reqs{5}  &            & \checkmark &            & \checkmark &            & \checkmark &            & \\
    \reqs{6}  &            & \checkmark &            & \checkmark &            & \checkmark & \checkmark & \\
    \reqs{7}  &            &            &            & \checkmark &            & \checkmark &            & \\
    \reqs{8}  &            &            &            & \checkmark &            &            &            & \\
    \reqs{9}  &            &            &            &            &            & \checkmark & \checkmark & \\
    \reqs{10} & \checkmark & \checkmark & \checkmark &            &            &            &            & \\
    \reqs{11} &            &            &            & \checkmark &            &            &            & \checkmark \\
    \reqs{12} &            &            &            & \checkmark &            &            &            & \checkmark \\
    \reqs{13} &            &            &            & \checkmark &            &            &            & \\
  \hline
\end{tabular}
     \caption{Requirements satisfaction for Acme software engineering process}
    \label{tab:RequirementsSatisfactionAcme}
\end{table*}

>>>>

In the previous Sect.~\ref{sec:model}, we demonstrated that our solution
satisfies all the challenge requirements. In this section, we summarize the
different techniques used to satisfy them, without repeating all the
justifications. We classify these techniques into three categories:
\begin{itemize}
    \item \emph{syntactic conformance}: the requirements are structurally
      satisfied when the model conforms to its metamodel

    \item \emph{constraints checking}: the requirements are fulfilled when all
      instances satisfy both syntactic conformance and the evaluation of
      invariants expressed for related concepts

    \item \emph{process tools}: the requirements are enforced by the
      implementation of the process tools illustrated by
      Fig.~\ref{fig:ToolingArchitecture}. It can be done by using behaviors
      defined in the models or by using the process tools manually.

\end{itemize}

@@

\renewcommand{\arraystretch}{1.1}
\begin{table*}
 \centering
 \rowcolors{4}{tableShade}{white}  %% start alternating shades from 3rd row
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
   \hline
    & \multicolumn{6}{c|}{Syntactic conformance} & Constraints & \multirow{2}{*}{Process tools}\\
   \cline{1-7}
                 & Conc.      & Spec.      & Comp.      & L.Inst.     & O.Inst.     & B.Mod.   &  checking & \\
  \hline
    \reqp{1}  & \checkmark &            & \checkmark &            &            &            &            & \\
    \reqp{2}  & \checkmark & \checkmark & \checkmark &            &            &            &            & \\
    \reqp{3}  &            &            & \checkmark &            &            &            &            & \\
    \reqp{4}  & \checkmark &            &            &            & \checkmark &            &            & \\
    \reqp{5}  & \checkmark &            & \checkmark &            &            &            &            & \\
    \reqp{6}  & \checkmark &            & \checkmark &            &  &            &            & \\
    \reqp{7}  & \checkmark &            & \checkmark &            &            &            &            & \\
    \reqp{8}  &            &            & \checkmark &            &            &            &            & \\
    \reqp{9}  &            &            & \checkmark &            &            &            & \checkmark & \\
    \reqp{10} & \checkmark &            &            &            & \checkmark &            &            & \\
    \reqp{11} & \checkmark &            & \checkmark &            & \checkmark &            &            & \\
    \reqp{12} &            &            & \checkmark &            &            &            &            & \\
    \reqp{13} & \checkmark &            & \checkmark &            & \checkmark &            &            & \\
    \reqp{14} & \checkmark &            &            &            & \checkmark &            &            & \\
    \reqp{15} & \checkmark &            &            &            & \checkmark &            &            & \\
    \reqp{16} & \checkmark &            &            &            & \checkmark &            &            & \\
    \reqp{17} & \checkmark           &            &            &            &            & \checkmark & \checkmark & \checkmark \\
    \reqp{18} & \checkmark           &            &            &            &            & \checkmark &            & \\
    \reqp{19} &            & \checkmark & \checkmark &            &            & \checkmark &            & \\
  \hline
\end{tabular}
     \caption{Requirements satisfaction for base metamodel}
    \label{tab:RequirementsSatisfactionBaseMetamodel}
\end{table*}

\begin{table*}
 \centering
  \rowcolors{4}{tableShade}{white}  %% start alternating shades from 3rd row
\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
   \hline
    & \multicolumn{6}{c|}{Syntactic conformance} & Constraints & \multirow{2}{*}{Process tools}\\
   \cline{1-7}
                 & Conc.      & Spec.      & Comp.      & L.Inst     & O.Inst     & B.Mod      & checking   & \\
  \hline
    \reqs{1}  &            &            &            & \checkmark &            &            &            & \\
    \reqs{2}  &            &            &            & \checkmark &            &            &            & \\
    \reqs{3}  & \checkmark & \checkmark & \checkmark & \checkmark &            &            &            & \checkmark \\
    \reqs{4}  & \checkmark & \checkmark & \checkmark & \checkmark &            &            &            & \\
    \reqs{5}  &            & \checkmark &            & \checkmark &            & \checkmark &            & \\
    \reqs{6}  &            & \checkmark &            & \checkmark &            & \checkmark & \checkmark & \\
    \reqs{7}  &            &            &            & \checkmark &            & \checkmark &            & \\
    \reqs{8}  &            &            &            & \checkmark &            &            &            & \\
    \reqs{9}  &            &            &            &            &            & \checkmark & \checkmark & \\
    \reqs{10} & \checkmark & \checkmark & \checkmark &            &            &            &            & \\
    \reqs{11} &            &            &            & \checkmark &            &            &            & \checkmark \\
    \reqs{12} &            &            &            & \checkmark &            &            &            & \checkmark \\
    \reqs{13} &            &            &            & \checkmark &            &            &            & \\
  \hline
\end{tabular}
     \caption{Requirements satisfaction for Acme software engineering process}
    \label{tab:RequirementsSatisfactionAcme}
\end{table*}
